Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-09-06 paper.tex
in the middle of checking roger's thesis

The signatures of vibronic coupling in the HDFG spectrum are made clear by using a simple model.
Using a two-well system described by $H = H_g |g) \left(g| + H_e |e\right) (e|$ where
\begin{subequations}\label{Hamiltonian}
	\begin{equation}
		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
	\end{equation}
	and
	\begin{equation}
		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\xi)^2 \right) + \hbar \omega_{eg}
	\end{equation}
\end{subequations}
for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).\cite{Carlson1988thesis}
System-bath interactions are neglected for this discussion.
For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\xi = 0.5$.
Note that $q = \sqrt{\frac{\omega}{\hbar}} Q$.
We assume the electronic state is both one and two photon allowed.

@@

\begin{table}[!htbp]
	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,0}$, $\ket{e,1}$, $\ket{e,2}$ for \autoref{Hamiltonian} with an offset $\xi = 0.5$.
	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here have been tabulated by Carlson.\cite{Carlson1988thesis}}
	\begin{ruledtabular}
		\begin{tabular}{cccc}
			$2\omega_2$ Electronic Resonance & $\ket{e,0}$ & $\ket{e,1}$ & $\ket{e,2}$\\
			\hline  
			$A$ 
			& $\langle 1 | 0 \rangle \langle 0 | 0 \rangle = 0.31 $  
			& $\langle 1 | 1 \rangle \langle 1 | 0 \rangle = 0.27 $ 
			& $\langle 1 | 2 \rangle \langle 2 | 0 \rangle = -0.04$\\

>>>>

The signatures of vibronic coupling in the HDFG spectrum are made clear by using a simple model.
Using a two-well system described by $H = H_g |g) \left(g| + H_e |e\right) (e|$ where
\begin{subequations}\label{Hamiltonian}
	\begin{equation}
		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
	\end{equation}
	and
	\begin{equation}
		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\xi)^2 \right) + \hbar \omega_{eg}
	\end{equation}
\end{subequations}
for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).
System-bath interactions are neglected for this discussion.
For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\xi = 0.5$.
Note that $q = \sqrt{\frac{\omega}{\hbar}} Q$.
We assume the electronic state is both one and two photon allowed.

@@

\begin{table}[!htbp]
	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,0}$, $\ket{e,1}$, $\ket{e,2}$ for \autoref{Hamiltonian} with an offset $\xi = 0.5$.
	The bra and ket labels are written according to their order in $A$, $B_1$, $B_2$ as written in \autoref{ABterms_DR}.
	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here are tabulated in the Supporting Information.}
	\begin{ruledtabular}
		\begin{tabular}{cccc}
			$2\omega_2$ Electronic Resonance & $\ket{e,0}$ & $\ket{e,1}$ & $\ket{e,2}$\\
			\hline  
			$A$ 
			& $\langle 1 | 0 \rangle \langle 0 | 0 \rangle = 0.31 $  
			& $\langle 1 | 1 \rangle \langle 1 | 0 \rangle = 0.27 $ 
			& $\langle 1 | 2 \rangle \langle 2 | 0 \rangle = -0.04$\\

### 2024-09-06 si.tex
in the middle of checking roger's thesis

By letting $\ket{m}$ belong to the ground state surface $|g)$ and $\ket{n}$ belong to the first excited surface $|e)$, we write\footnote{Note that any instance of $\int \mathrm{d}q f(q) \equiv \int_{-\infty}^{\infty} \mathrm{d}q f(q)$.}
\begin{equation}
\begin{split}
		\mel{n}{q^k}{m} &= \int \mathrm{d}q \psi^*_n(q+\Delta) q^k \psi_m(q)\\
		&= \int \mathrm{d}q N(n) N(m) H_n(q+\Delta) \exp(-\frac{(q + \Delta)^2}{2}) q^k H_m(q) \exp(-\frac{q^2}{2})
\end{split}
\end{equation}
Introducing $\tilde{N} \equiv N(n)N(m)$ and slightly rearranging, we see
\begin{equation}\label{key}
	\mel{n}{q^k}{m} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q H_n(q+\Delta) q^k H_m(q) \exp(-q^2 - q\Delta)
\end{equation}
This is the key result.
As a side note, \autoref{key} explicitly shows
\begin{subequations}
	\begin{equation}
		\lim_{\Delta \rightarrow 0} \langle n | m \rangle = \delta_{n,m}
	\end{equation}
and
	\begin{equation}
	\lim_{\Delta \rightarrow 0} \mel{n}{q}{m} = \sqrt{\frac{1}{2}} \left(\sqrt{m}\delta_{n,m-1} + \sqrt{m+1} \delta_{n,m+1}\right)
	\end{equation}
\end{subequations}
i.e., as the offset vanishes, the normal harmonic oscillator selection rules are obtained, the expected result, where $\delta$ is the Kronecher delta.

It is well known that the Hermite polynomials $H_v(q)$ are linear combinations of $q^w$, $w \in \mathbf{N}$. 
Thus, evaluating \autoref{key} for arbitrary $m,n,k$ values resolves into evaluating sums of integrals of the form
\begin{equation}\label{integral}
	\int \mathrm{d}q \ q^w \exp(-q^2 - q\Delta)
\end{equation}
When $w=0$, the result is trivial:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		\int \mathrm{d}q \exp(-q^2 - q\Delta) &= \int \mathrm{d}q \exp(-(q^2 + q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int \mathrm{d}q \exp(-(q + \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}
 For $w \neq 0$, \autoref{integral} is evaluated through repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\int \mathrm{d}q \ q^w \exp(-q^2 - q\Delta) = -\partial_{\Delta} \int \mathrm{d}q \ q^{w-1} \exp(-q^2 - q\Delta)
\end{equation}

We now have the background needed to calculate $\mel{1}{q}{0}$ for an arbitrary offset $\Delta$.
We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of arbitrary curvature,\cite{Myers1982} so we focus our attention onto Herzberg-Teller integrals, which are not commonly tabulated.
Starting with \autoref{key},
\begin{equation}
\begin{split}
	\mel{1}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q H_1(q+\Delta) q H_0(q) \exp(-q^2 - q\Delta)
\end{split}
\end{equation}
Using $H_0(q) = 1$ and $H_1(q) = 2q$,\cite{RN230} 
\begin{equation}\label{HT10}
	\begin{split}
		\mel{1}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q \ 2(q + \Delta) q \exp(-q^2 - q\Delta)\\
		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q \ (q^2 + q \Delta) \exp(-q^2 - q\Delta)\\
		&=  2\tilde{N} \exp(-\frac{\Delta^2}{2}) \left(\int \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) + 2\Delta \int \mathrm{d}q \ q \exp(-q^2 - q\Delta) \right)
	\end{split}
\end{equation}
These integrals are now easily evaluated using \autoref{identity}:
\begin{subequations}\label{evalGaussians}
	\begin{equation}
		\begin{split}
					\int \mathrm{d}q \ q \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
					& = -\sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
		\end{split}
	\end{equation}
giving
\begin{equation}
	\begin{split}
		\int \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(-\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
	\end{split}
\end{equation}
\end{subequations}
With $\tilde{N} = N(1)*N(0) = (1! \ 2^1 \pi^{\frac{1}{2}})^{-\frac{1}{2}} * (0! \ 2^0 \pi^{\frac{1}{2}})^{-\frac{1}{2}} = \sqrt{1/2\pi}$ and substituting the results of \autoref{evalGaussians} into \autoref{HT10}, 
\begin{equation}
	\mel{1}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
\end{equation}
The evaluation of other Herzberg-Teller integrals follows a similar process.
These results have been tabulated by Carlson. \cite{Carlson1988thesis}

>>>>

By letting $\ket{m}$ belong to the ground state surface $|g)$ and $\ket{n}$ belong to the first excited surface $|e)$, we write
\begin{equation}
\begin{split}
		\mel{n}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \psi^*_n(q-\Delta) q^k \psi_m(q)\\
		&= \int_{-\infty}^\infty \mathrm{d}q N(n) N(m) H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k H_m(q) \exp(-\frac{q^2}{2})
\end{split}
\end{equation}
Introducing $\tilde{N} \equiv N(n)N(m)$ and slightly rearranging, we see
\begin{equation}\label{key}
	\mel{n}{q^k}{m} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_n(q+\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
\end{equation}
This is the key result.
As a side note, \autoref{key} explicitly shows
\begin{subequations}
	\begin{equation}
		\lim_{\Delta \rightarrow 0} \langle n | m \rangle = \delta_{n,m}
	\end{equation}
and
	\begin{equation}
	\lim_{\Delta \rightarrow 0} \mel{n}{q}{m} = \sqrt{\frac{1}{2}} \left(\sqrt{m}\delta_{n,m-1} + \sqrt{m+1} \delta_{n,m+1}\right)
	\end{equation}
\end{subequations}
i.e., as the offset vanishes, the normal harmonic oscillator selection rules are obtained, the expected result, where $\delta$ is the Kronecher delta.

It is well known that the Hermite polynomials $H_v(q)$ are linear combinations of $q^w$, $w \in \mathbf{N}$. 
Thus, evaluating \autoref{key} for arbitrary $m,n,k$ values resolves into evaluating sums of integrals of the form
\begin{equation}\label{integral}
	\int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta)
\end{equation}
When $w=0$, the result is trivial:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		\int_{-\infty}^\infty \mathrm{d}q \exp(-q^2 + q\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 + q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}
 For $w \neq 0$, \autoref{integral} is evaluated through repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta)
\end{equation}

We now have the background needed to calculate $\mel{1}{q}{0}$ for an arbitrary offset $\Delta$.
We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of arbitrary curvature,\cite{Myers1982} so we focus our attention onto Herzberg-Teller integrals, which are not commonly tabulated.
Starting with \autoref{key},
\begin{equation}
\begin{split}
	\mel{1}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_1(q+\Delta) q H_0(q) \exp(-q^2 - q\Delta)
\end{split}
\end{equation}
Using $H_0(q) = 1$ and $H_1(q) = 2q$,\cite{RN230} 
\begin{equation}\label{HT10}
	\begin{split}
		\mel{1}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q + \Delta) q \exp(-q^2 - q\Delta)\\
		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ (q^2 + q \Delta) \exp(-q^2 - q\Delta)\\
		&=  2\tilde{N} \exp(-\frac{\Delta^2}{2}) \left(\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) + 2\Delta \int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 - q\Delta) \right)
	\end{split}
\end{equation}
These integrals are now easily evaluated using \autoref{identity}:
\begin{subequations}\label{evalGaussians}
	\begin{equation}
		\begin{split}
					\int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
					& = -\sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
		\end{split}
	\end{equation}
giving
\begin{equation}
	\begin{split}
		\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(-\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
	\end{split}
\end{equation}
\end{subequations}
With $\tilde{N} = N(1)*N(0) = (1! \ 2^1 \pi^{\frac{1}{2}})^{-\frac{1}{2}} * (0! \ 2^0 \pi^{\frac{1}{2}})^{-\frac{1}{2}} = \sqrt{1/2\pi}$ and substituting the results of \autoref{evalGaussians} into \autoref{HT10}, 
\begin{equation}
	\mel{1}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
\end{equation}
The evaluation of other Herzberg-Teller integrals follows a similar process, or by using symbolic manipulation packages. 
The relevant Franck-Condon factors and Herzberg-Teller integrals, assuming identical curvature and no Duschinsky coupling, are tabulated below.

\begin{table}[!htbp]
	\caption{\label{T:FC Integral} Franck-Condon Factors.}
	\begin{ruledtabular}
		\begin{tabular}{cc}
			$\mel{n}{0}{m}$ & Expression\\
			\hline  
			$A$ & $\langle 1 | 0 \rangle \langle 0 | 0 \rangle = 0.31 $  \\

			$B_1$ & $\langle 1 | 0 \rangle \mel{0}{Q}{0} = -0.08$ \\

			$B_2$ & $\mel{1}{Q}{0} \langle 0 | 0 \rangle = 0.55$\\
		\end{tabular}
	\end{ruledtabular}
\end{table}

\begin{table}[!htbp]
	\caption{\label{T:HT Integral} Franck-Condon Factors.}
	\begin{ruledtabular}
		\begin{tabular}{cc}
			$\mel{n}{q}{m}$& Expression\\
			\hline  
			$\mel{0}{q}{0}$ & $\frac{\Delta}{2} \exp(-\Delta^2/4)$  \\ 
			$\mel{1}{q}{0}$ & $\frac{1}{\sqrt{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
			$\mel{2}{q}{0}$ & $\frac{1}{\sqrt{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
			$\mel{0}{q}{1}$ & $\frac{1}{\sqrt{2}} \exp(-\Delta^2/4)(1 + \Delta^2/2) $ \\
			$\mel{1}{q}{1}$ & $\frac{\Delta}{{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
			$\mel{2}{q}{1}$ & $\frac{\Delta}{{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
			$\mel{1}{q}{1}$ & $\frac{\Delta}{{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\

		\end{tabular}
	\end{ruledtabular}
\end{table}
